TSELM: Target speaker extraction using discrete tokens and language models \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-09-06 src/paper.tex
update

\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract. 
\end{abstract}

>>>>

\begin{abstract}
We present TSELM, a novel target speaker extraction network using discrete tokens and language models. This model utilizes multiple discretized layers
of WavLM Large as input tokens. It uses cross attention to inject target speaker information and language models to model the sequences. 
\end{abstract}
